---
title: "Qudratic Equation Lesson"
format: pdf
---

# Quadratic Equation Lesson

In this lesson, we will explore how to apply the quadratic equation and graphically demonstrate the correctness of the solution.

## Define variables

-   We'll use **d** instead of `c` to avoid conflicts with the reserved function name in R.

\[ a = 1, b = 3, d = 2 \]

## Quadratic Equation

The quadratic equation is given by:

$f(x) = ax^2 + b + d = 0$

Let's calculte the solutions to this equation.

```{r}
# Define the quadratic equation coefficients
a <- 1
b <- 3
d <- 2

# Calculate the discriminant
discriminant <- b^2 - 4*a*d

# Check if the discriminant is non-negative (real solutions)
if (discriminant >= 0) {
  # Calculate the solutions
  x1 <- (-b + sqrt(discriminant)) / (2*a)
  x2 <- (-b - sqrt(discriminant)) / (2*a)

# Print the solutions
  cat("Solutions: x1 =", x1, ", x2 =", x2, "\n")
} else {
  cat("The quadratic equation has no real solutions.\n")
}


```

## Graph

```{r}
# Generate x values for plotting the quadratic function
x_values <- seq(-3, 3, length.out = 100)
y_values <- a * x_values^2 + b * x_values + d

# Plot the quadratic function
plot(x_values, y_values, type = "l", col = "blue", lwd = 2, main = "Quadratic Equation Graph",
     xlab = "x", ylab = "f(x)", ylim = c(min(y_values) - 2, max(y_values) + 2))
grid()


```
